My title

### 2024-12-01 paper/paper.qmd
Edits to model and data

library(tidyverse)
library(dplyr)
library(janitor)
library(lubridate)
library(modelsummary)
library(rstanarm)
library(knitr)
library(bayesplot)
```

@@

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

```{r}
bay_model <- stan_glm(
  MVP_index ~ PTS + AST + TRB + BLK + STL + WS,
  data = nba_master,
   family = gaussian(),
  prior = normal(0, 5),
  prior_intercept = normal(0, 5),
  chains = 4,
  iter = 2000,
  warmup = 1000,
  cores = 4,
  control = list(adapt_delta = 0.95),
  seed = 613
)

>>>>

library(tidyverse)
library(dplyr)
library(janitor)
library(lubridate)
library(modelsummary)
library(rstanarm)
library(knitr)
library(bayesplot)
library(StanHeaders)
library(Matrix)
library(lme4)

@@

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \pi_i + \alpha_i + \rho_i + \beta_i + \xi_i + \omega_i \\
\mu &\sim \mbox{Normal}(0, 2.5) \\
\pi &\sim \mbox{Normal}(0, 2.5) \\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\rho &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\xi &\sim \mbox{Normal}(0, 2.5) \\
\omega &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

```{r}
# Fit a linear regression model
glm_model <- glm(MVP_index ~ PTS + AST + TRB + BLK + STL + WS, data = nba_master)

# View the summary of the model
summary(lm_model)

plot(lm_model)
```
